\textbf{Honeypot Assignment: \\ \emph{Group Contagiarium}}

### 2012-01-10 Paper_honeypot.tex
Conclusion edit

Only three real scans took place, as reported in the Section Connections between attacks. Unfortuntaly we did not make our honeypot interesting enough for them to return and actually break in.

Our chose for swiching from a Low Interaction to a High Interaction honeypot seems like a good tactic, but due to downtime and bugged software, we did not have enough time.

Concluding: we did see some people checking us out, but noone actually broke in. For further research we suggest using the same setup, but having the server online for a much longer time.

@@

Two of the team members had limited Linux experience. It took some time for them to understand how Linux commandline works. Fortunately we had two guru's in the group that were able to teach the newbies.

@@

The Google Hack Honeypot was supposed to attract hackers. Unfortunately it soon crashed due to unknown configuration errors. Because the results in the period the tool was running were non-existent and we were switching to HI later on, we decided not to use it.

>>>>

Only three real scans took place, as reported in the Section Connections between attacks. Unfortunately we did not make our honeypot interesting enough for them to return and actually break in.

Our choice for swiching from a Low Interaction to a High Interaction honeypot seems like a good tactic, but due to the low activity we did not have enough time to collect significant results.

Concluding: we did see a lot of probing activity, but no one actually broke in.
%For further research we suggest using the same setup, but having the server online for a much longer time.
We would like to continue a similar setup for research purposes privately.

@@

Two of the team members had limited Linux experience. It took some time for them to understand how Linux command line works. Fortunately we had two guru's in the group that were able to teach the newbies.

@@

The Google Hack Honeypot was supposed to entice hackers. Unfortunately it soon crashed due to unknown configuration errors. Because the results in the period the tool was running were non-existent and we were switching to HI later on, we decided not to use it.

\item Lack of tools

There exists a significant lack of tools to stealthily audit HI Linux honeypot activity, and as can by Project Honeynet's Google summer of Code project, a lack of graphing tools for network data.
For this paper we invented our own using Python and Gnuplot.
